Physcraper: a python package for continual update of evolutionary estimates using the Open Tree of Life

### 2020-07-14 2-body.Rmd
figure 1

The general workflow is described in FIGURE. Next, we will describe the technical details of each step.

@@

<!-- ```{bash echo= FALSE, include=FALSE, message= FALSE, results='hide'}
wget "https://raw.githubusercontent.com/McTavishLab/physcraperex/master/data-raw/malvaceae-images/cotree-plot2-1.png"
mv cotree-plot2-1.png docs/figs/cotree-plot2-1.png
``` -->
```{r fig-2, echo=FALSE, fig.cap="Comparison of original tree and tree updated with Physcraper, family Malvaceae.", out.width = '85%', fig.retina= 2, fig.align = "center"}
knitr::include_graphics("docs/figs/cotree-plot2-1.png")
```
\newpage

>>>>

```{r framework, echo=FALSE, fig.cap="Physcraper general framework.", out.width = '85%', fig.retina= 2, fig.align = "center"}
knitr::include_graphics("https://raw.githubusercontent.com/McTavishLab/physcraper/pyopensci/docs/img/schematic.svg")
# knitr::include_graphics("docs/figs/schematic.svg")
```

The Physcraper software is fully described on its documentation website at https://physcraper.readthedocs.io/en/latest/, along with installation, tutorials, examples and function usage.
The general Physcraper workflow is shown in Figure \@ref(fig:framework). Next, we will describe the technical details of each step of the workflow.

@@

<!-- ```{bash echo= FALSE, include=FALSE, message= FALSE, results='hide'}
wget "https://raw.githubusercontent.com/McTavishLab/physcraperex/master/data-raw/malvaceae-images/cotree-plot2-1.png"
mv cotree-plot2-1.png docs/figs/cotree-plot2-1.png
``` -->
```{r malvaceae, echo=FALSE, fig.cap="Comparison of original tree and tree updated with Physcraper, family Malvaceae.", out.width = '85%', fig.retina= 2, fig.align = "center"}
knitr::include_graphics("docs/figs/cotree-plot2-1.png")
```
\newpage

### 2020-07-14 docs/submission-mee-2020-07-13.tex
figure 1

\textbf{Word count}: 3694

@@

The general workflow is described in FIGURE. Next, we will describe the technical details of each step.

@@

\caption{Comparison of original tree and tree updated with Physcraper, family Malvaceae.}\label{fig:fig-2}
\end{figure}
\newpage

>>>>

\textbf{Word count}: 3722

@@

{\centering \includegraphics[width=0.85\linewidth]{docs/figs/schematic}

\caption{Physcraper general framework.}(\#fig:framework)
\end{figure}

The Physcraper software is fully described on its documentation website at \url{https://physcraper.readthedocs.io/en/latest/}, along with installation, tutorials, examples and function usage.
The general Physcraper workflow is shown in Figure @ref(fig:framework). Next, we will describe the technical details of each step of the workflow.

@@

\caption{Comparison of original tree and tree updated with Physcraper, family Malvaceae.}(\#fig:malvaceae)
\end{figure}
\newpage

### 2020-07-14 render2-mee.tex
figure 1

\caption{Physcraper general framework.}(\#fig:framework)
\end{figure}

The Physcraper software is fully described on its documentation website at \url{https://physcraper.readthedocs.io/en/latest/}, along with installation, tutorials, examples and function usage.
The general Physcraper workflow is shown in Figure @ref(fig:framework). Next, we will describe the technical details of each step of the workflow.

@@

\caption{Comparison of original tree and tree updated with Physcraper, family Malvaceae.}(\#fig:malvaceae)
\end{figure}
\newpage

>>>>

\caption{Physcraper general framework.}\label{fig:framework}
\end{figure}

The Physcraper software is fully described on its documentation website at \url{https://physcraper.readthedocs.io/en/latest/}, along with installation, tutorials, examples and function usage.
The general Physcraper workflow is shown in Figure \ref{fig:framework}. Next, we will describe the technical details of each step of the workflow.

@@

\caption{Comparison of original tree and tree updated with Physcraper, family Malvaceae.}\label{fig:malvaceae}
\end{figure}
\newpage
